%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \documentclass[]{resume}
 
     \begin{document}
     
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %
  %     Profile
  %
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
\namesection{Souptik} {Datta}\infoline{\href{mailto:souptikdatta2001@gmail.com}{souptikdatta2001@gmail.com} | 8334012176 | \href{https://github.com/Souptik2001}{\textbf{GitHub}} | \href{https://www.linkedin.com/in/souptik-datta}{Linkedin | }} | \href{https://souptik.dev/}{\textbf{Blog}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

    \runsubsection{\href{https://kiit.ac.in/}{Kalinga Institute Of Industrial Technology, Odisha, India}}\hspace*{\fill}  \location{April 2019 - April 2023}

    B.Tech, Electronics And Telecommunications, \textit{CGPA: 8.75/10}\hspace*{\fill}

    \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
       %
       %     Experience
       %
       %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
       \section{Experience}
       \raggedright
         
           \runsubsection{\large{\href{https://rtcamp.com}{rtCamp}}} - \textit{Software Engineer → Senior Software Engineer}\hspace*{\fill}  \location{Jan ‘22 - Jul ‘24, Jul ‘24 - Present}

            \textbullet\ Management - Working as Engineering lead for a project; responsibilities including initial engineering discovery for tasks, code reviews, usual development and DevOps activities.

            \textbullet\ Front-end - Create lightweight and scalable web-components ensuring reusability, compatibility, and performance. 

            \textbullet\ Front-end - Crafted tailored solutions for Gutenberg using \textbf{ReactJS}, such as custom \textbf{Gutenberg blocks}, custom \textbf{RichText format}, and also \textbf{extending the Gutenberg editor} for custom functionalities.

            \textbullet\ Backend - Developed efficient backend solutions using PHP, including designing and building REST APIs, integrating and utilizing data from third-party APIs, media-management solutions, creating utility scripts, and migrating CLI scripts.

            \textbullet\ Backend - Worked on developing a \textbf{GraphQL layer} acting as a middleware between WordPress and a React frontend, to effectively consume data from WordPress and serve to the frontend. And yes, mutations to push data from frontend to backend!

            \textbullet\ Devops - Managed hosting and deployment cycles of enterprise WordPress applications on different platforms ranging from \textbf{self-managed servers} to \textbf{WordPress VIP}.

            \textbullet\ Management - Directly involved with the Learning \& Development team to train and mentor new trainees in both technical and behavioral aspects, which involved conducting technical sessions, code reviews, and reporting detailed consumable feedback.
           \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
\descript{Programming Languages} & {\location{\textbf{PHP}, \textbf{Javascript}, Python, C++}} \\
\descript{Front-end} & {\location{\textbf{Vanilla stack}, \href{https://developer.mozilla.org/en-US/docs/Web/API/Web_components}{\textbf{Web-components}}, \textbf{ReactJS}, NextJS}} \\
\descript{Tools/Frameworks} & {\location{PHPUnit, PHPStan, PHPCS, ESLint, Jest}} \\
\descript{Databases} & {\location{\textbf{MySQL}, MongoDB, \textbf{Redis}}} \\
\descript{CMS} & {\location{WordPress}} \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
       %
       %     Projects
       %
       %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
       \section{Personal Projects}
       \raggedright

           \runsubsection{\large{Decoupled WordPress Solutions}} [\textbf{\href{https://souptik.dev}{\faIcon{link}}}][\textbf{\href{https://github.com/Souptik2001/Souptik2001.github.io}{\faIcon{github}}}][\textbf{\href{https://github.com/Souptik2001/wp-decoupled-sample}{\faIcon{github-alt}}}] - \textit{ReactJS, WordPress, GraphQL}

           The first one is my personal blogging site and the second one is a skeleton decoupled project. Both architectures are almost similar with some differences in the GraphQL data fetching layer.\\

           \sectionsep

           \runsubsection{\large{WordPress Local Development Bootstrap}}
           [\textbf{\href{https://github.com/Souptik2001/wordpress.setup}{\faIcon{github}}}] - \textit{Bash, Jinja, Python}

           Simple yet powerful automated bash script to setup WordPress local development setup with Lando (docker-based local development setup).

           \sectionsep


     \ 
     \end{document}
